Nature or Nurture? Collisionless Evolution of Galactic Disc-Halo Systems

### 2019-07-19 Thesis/Thesis.tex
Semi-final presubmission draft
Night before submission. Likely final pre-submission draft. Checked for spelling issues.

I am grateful for the years of friendship with my fellow astronomy graduate students. In their own ways, they have all kept me mostly sane for 4 years. I would not have been able to perservere without their support. Although they did not succeed in turning me into a Canadian, they did manage to make me grow a beard. I look forward to many more years of friendship.

@@

\chapter*{List of Abreviations}
\begin{longtable}{ll} 
\hline
Abbreviation & Expansion \\ \hline
\textsc{AGAMA} & Action-based Galaxy Modelling Architecture \\
DF & Distribution Function \\
F(L)RW & Friedmann (Lema\^itre) Robertson Walker\\
LAMOST & Large Sky Area Multi-Object Fiber Spectroscopic Telescope \\
M31 & Messier object 31 (Andromeda) \\
M33 & Messier object 33\\
NFW & Navarro-Frenk-White\\
RAVE & Radial Velocity Experiment \\
SDSS & Sloan Digital Sky Survey\\
Sgr dSph & Sagittarius Dwarf Spheroidal [Galaxy]\\
Sgr  & [The] Sagittarius [Stream]\\ \hline
\end{longtable}

@@

% Include my chapter texts - kept separated to make editing easier.
%\include{Glossary}
\include{Introduction}
\include{Background}
\include{Paper_I}
\include{Implementation}
\include{Paper_II}
\include{Paper_III}

>>>>

I am grateful for the years of friendship with my fellow astronomy graduate students. In their own ways, they have all kept me mostly sane for 4 years. I would not have been able to persevere without their support. Although they did not succeed in turning me into a Canadian, they did manage to make me grow a beard. I look forward to many more years of friendship.

@@

\chapter*{List of Abreviations}
\begin{longtable}{ll} 
\hline
Abbreviation & Expansion \\ \hline
\textsc{AGAMA} & Action-based Galaxy Modelling Architecture \\
DF & Distribution Function \\
F(L)RW & Friedmann (Lema\^itre) Robertson Walker\\
GMC    & Giant Molecular Cloud\\
LAMOST & Large Sky Area Multi-Object Fiber Spectroscopic Telescope \\
LMC & Large Magellanic Cloud\\
M31 & Messier object 31 (Andromeda) \\
M33 & Messier object 33\\
NFW & Navarro-Frenk-White\\
RAVE & Radial Velocity Experiment \\
SDSS & Sloan Digital Sky Survey\\
Sgr dSph & Sagittarius Dwarf Spheroidal [Galaxy]\\
Sgr  & [The] Sagittarius [Stream]\\ 
SMC  & Small Magellanic Cloud  \\ \hline
\end{longtable}

@@

% Include my chapter texts - kept separated to make editing easier.
%\include{Glossary}
\include{Introduction}
\include{Background}
\include{Paper_I}
%\include{Implementation}
\include{Paper_II}
\include{Paper_III}
